---
title: "Modeling Results for Roediger and Karpicke 2006a Exp. 1 Data"
author: "Will Hopper"
output: html_document
---

```{r knitr_setup, cache=FALSE,echo=FALSE, warning=F, include=FALSE, message=FALSE}
library(knitr)
library(pander)
library(ggplot2)
library(reshape2)
library(xtable)
opts_chunk$set(echo = FALSE,fig.width=11,fig.height=7,cache=FALSE, 
               warning=F, message=FALSE, fig.align='center')
if(.Platform$OS.type == "unix") {
  root <- Sys.getenv("HOME")
}   else if (.Platform$OS.type == "windows") {
  root <- Sys.getenv("USERPROFILE")
}
setwd(file.path(root,"Documents","CEMNL","Testing and Recovery","modeling","R_and_K_2006a","SAMRL"))
read_chunk(file.path('plotSAMRL.R'))
```

```{r herp}
<<get_fits>>
```

# Model 1 - Recovery Learning, Recovery Dependence
Codename: *MUNCHLAX*
```{r p}
<<fits_only>>
  print(p1)
```

```{r params,results='asis'}
print(xtable(params[1,],digits=c(1,4,4,4,4,4,4,0,0),caption = "Parameters"),
      type = "html",include.rownames=FALSE,caption.placement="top")
```

<br>
$X^2$ = `r round(err,3)`

Predictions using best fit parameters of *MUNCHLAX*, allowing for independent recovery attemptes at every time point after practice test
```{r new}
<<one_new_context>>
    print(p2)
```

Predictions using best fit parameters of *MUNCHLAX*, never allowing a new independent recovery attempt after practice test
```{r old}
<<one_old_context>>
  print(p3)
```

Predictions using best fit parameters of *MUNCHLAX*, allowing a new independent recovery attempt only after initial final test
```{r mixed}
<<switch_context>>
  print(p4)
```