---
title: "Modeling Results for Roediger and Karpicke 2006a Exp. 1 Data"
author: "Will Hopper"
output: html_document
---

```{r knitr_setup, cache=FALSE,echo=FALSE, warning=F, include=FALSE, message=FALSE}
library(knitr)
library(pander)
library(ggplot2)
library(reshape2)
opts_chunk$set(echo = FALSE,fig.width=11,fig.height=7,cache=FALSE, 
               warning=F, message=FALSE, fig.align='center')
if(.Platform$OS.type == "unix") {
  root <- Sys.getenv("HOME")
}   else if (.Platform$OS.type == "windows") {
  root <- Sys.getenv("USERPROFILE")
}
setwd(file.path(root,"Documents","CEMNL","Testing and Recovery","models","datasets", "R_and_K_2006a"))
read_chunk(file.path('plot_SAM.R'))
```

```{r herp}
<<get_fits>>
```

# Model 1 - Recovery Learning, Recovery Dependence
Codename: *SNORLAX*
```{r p}
<<fits_only>>
  print(p1)
```

Predictions using best fit parameters of *SNORLAX*, allowing for independent recovery attemptes at every time point after practice test
```{r new}
<<one_new_context>>
    print(p2)
```

Predictions using best fit parameters of *SNORLAX*, never allowing a new independent recovery attempt after practice test
```{r old}
<<one_old_context>>
  print(p3)
```

Predictions using best fit parameters of *SNORLAX*, allowing a new independent recovery attempt only after initial final test
```{r mixed}
<<switch_context>>
  print(p4)
```